Equivalence Hypergraphs: E-Graphs for Monoidal Theories

### 2024-09-30 closed_monoidal/closed_monoidal.tex
small fix

Since a component of a natural transformation $\overline{\alpha}$ between two $\catname{SLat}$-enriched functors $\overline{F} : \enriched{C} \to \enriched{D}$ and $\overline{G}: \enriched{C} \to \enriched{D}$ has the form $\overline{\alpha_{A}} : I_{\catname{SLat}} \to \enriched{D}(FA, GA)$, it can be identified with the element of $\enriched{D}(FA,GA)$, i.e. we can use the syntax for plain morphism to depict components of natural transformations.
This allows us to reuse the whole syntax machinery for Cartesian closed categories for their free $\catname{SLat}$-enriched version which induce an additional equation

>>>>

Since a component of a natural transformation $\overline{\alpha}$ between two $\catname{SLat}$-enriched functors $\overline{F} : \enriched{C} \to \enriched{D}$ and $\overline{G}: \enriched{C} \to \enriched{D}$ has the form $\overline{\alpha_{A}} : I_{\catname{SLat}} \to \enriched{D}(FA, GA)$, it can be identified with the element of $\enriched{D}(FA,GA)$, i.e. we can use the syntax for plain morphism to depict components of natural transformations.
This means, in particular, that given a usual adjuntion $\mathcal{C}(A \otimes X, Y) \cong \mathcal{D}(A, X \multimap Y)$ with respetive natural transformations $\eta : I \to X \multimap (- \otimes X)$ and $\varepsilon : (X \multimap -) \otimes X \to I$ that define a Cartesian closed monoidal category, we can reuse the graphical syntax introduced in~\cite{GhicaZanassiStringLambda}
for depicting morphisms in a freely $\catname{SLat}$-enriched Cartesian closed monoidal categories.
Free enrichment induces an additional equation for \textit{abstraction} box below.
